Inter-organizational business processes involve multiple independent organizations collaborating to achieve mutual interests. 
Process mining techniques have the potential to allow these organizations to enhance operational efficiency, improve performance, and deepen the understanding of their business based on the recorded process event data. 
However, inter-organizational process mining faces substantial challenges, including topical secrecy concerns: The involved organizations may not be willing to expose their own data to run mining algorithms jointly with their counterparts or third parties. 
In this paper, we introduce a novel approach that unlocks process mining on multiple actors' process event data while safeguarding the secrecy and integrity of the original records in an inter-organizational business setting.
To ensure that the data acquisition, merging and elaboration phases are secure and that the processed information is hidden from involved and external actors alike, our approach resorts to decentralized trusted applications running in Trusted Execution Environments (TEEs).
We show the feasibility of our solution by showcasing its application to a healthcare scenario.
%
\begin{comment}% Original abstract
 Through process mining tecniques, organizations enhances their operational efficiency, improve performances, and deepen the understanding of their business processes. While most process mining research focuses on intra-organizational settings, the emerging importance of inter-organizational collaborations for operational excellence cannot be ignored. Inter-organizational business processes involve multiple independent organizations collaborating to achieve mutual interests. However, inter-organizational process mining faces substantial challenges, primarily centered on confidentiality concerns. In this paper, we introduce a novel approach based on the adoption of trusted applications running in Trusted Execution Environments (TEEs). Our research work aims at ensuring privacy preservation and safeguarding the integrity of sensitive information during process mining procedures in inter-organizational contexts. Therefore, we introduce a TEE-based infrastructure supporting the execution of trusted applications through which partner organizations securely share operational information and apply process mining techniques. We show the feasibility of our solution by exposing an healthcare scenario that serve as running example. Our contribution includes a discussion of the proposed research work that addresses strengths and areas for improvement.
\end{comment}
